\documentclass{scrartcl}
\usepackage{vhistory}  % version history at end of document
\usepackage{hyperref}  % hyper references

\newcommand{\docTitle}{How to Install TeXstudio}
\newcommand{\MEK}{Matt Kontz}

\hypersetup{%
 	pdftitle = {\docTitle},
	pdfkeywords = {\docTitle, Version \vhCurrentVersion
	from \vhCurrentDate},
	pdfauthor = {\vhListAllAuthorsLong}
}

\usepackage{scrpage2}
\pagestyle{scrheadings}
\ihead{\docTitle\ -- Version \vhCurrentVersion}
\chead[]{}
%\ohead[\thepage]{\thepage}
%\ifoot{\docTitle\ -- Version \vhCurrentVersion}
\cfoot[\thepage]{\thepage}
%\ofoot[\thepage]{\thepage}

\begin{document}

\title{\docTitle}
\author{\vhListAllAuthors}
\date{Version \vhCurrentVersion\ from \vhCurrentDate}
\maketitle

\section{Summary}
This document was created to briefly described the steps require to setup TeXstudio on both Windows and Ubuntu operating systems.


\section{Install MiKTex}
\label{sec:install_MiKTeX}

\href{https://miktex.org}{MiKTeX} (pronounced mick-tech) is an up-to-date implementation of TeX/LaTeX and related programs.

\subsection{Windows} 
\label{ssec:install_MiKTeX_windows}

\begin{enumerate}
	\item Download executable from \href{https://miktex.org/download}{miktex.org/download}
	\item Run executable and follow directions.
\end{enumerate}

\section{Install TeXstudio}
\label{sec:install_TeXstudio}

\href{https://www.texstudio.org/#home}{TeXstudio} is an integrated writing environment for creating LaTeX documents.

\subsection{Windows}
\label{ssec:install_TeXstudio_windows}

\begin{enumerate}
	\item Install LaTeX package manager MiKTeX
	\item Download executable from \href{https://www.texstudio.org/#download}{www.texstudio.org}
	\item Run executable and follow directions.
\end{enumerate}

\subsection{Ubuntu} 
\label{ssec:install_TeXstudio_ubuntu}

\begin{enumerate}
	\item Install full version of TexLive \\ $\qquad >>$ sudo apt install texlive-full
	\item Install TeXstudio \\ $\qquad >>$ sudo apt-get install texstudio
\end{enumerate}

\begin{versionhistory}
\vhEntry{1.0}{Dec 5, 2018}{\MEK}{Created initial version with brief directions on installing MiKTeX and TeXstudio in Windows.}
\vhEntry{1.1}{Dec 7, 2018}{\MEK}{Update header and footers.}
\vhEntry{1.2}{Dec 8, 2018}{\MEK}{Added brief directions on installing TeXstudio with TexLine on Ubuntu.}
\end{versionhistory}

\end{document}
